# fetch

# cloned copy - practical 4

---
title: "Exercise 3"
format: html
editor: visual
---

BREAK SOMETHING

```{r}
library(palmerpenguins)
library(dplyr)

mean_mass_by <- function(data, group_var) {
  data |>
    group_by({{group_var}}) |>
    summarise(mean_mass = mean(body_mass_g, na.rm = TRUE))
}

mean_mass_by(penguins, species)
```

**Expected to do:** calculate the mean mass of penguins grouped by species

**What might go wrong:** group_var is not treated as an variable that will be inserted but as an actual "name".

```{r}
library(palmerpenguins)
library(dplyr)
 
summarise_species <- function(data) {
  data |>
    group_by(species) |>
    summarise(mean_mass = mean_body_mass(body_mass_g))
}
 
mean_body_mass <- function(x) {
  mean(x, na.rm = TRUE)   
}
 
summarise_species(penguins)

```

```{r}
my_factorial <- function(n) {
  stopifnot( n >= 0, n == as.integer(n))
  if (n <= 1) return(1)
  return(n * my_factorial(n - 1))
}

my_factorial(5)   # returns 120 — correct
my_factorial(0)   # hangs / errors
my_factorial(3.5) # also wrong
```

```{r}
standardise <- function(x) {
  (x - mean(x, na.rm = TRUE)) / sd(x, na.rm = TRUE)
}

standardise(c(1, 2, 3, 4, 5))   # fine
standardise(c(1, 2, NA, 4, 5))  # returns all NAs — why?
```

**debugonce()** enters debugging once after the function is called and then never again.

**debug(standardise)** enters debugging everytime the function standardise is called. To not enter debugging after calling standardise you have to call undebug(standardise)

**Scenario where debug() is prefered over debugonce():**

When fixing a bug and planning on calling the function many times over.

You are debugging `standardise()` inside a larger analysis pipeline, and each small code change requires rerunning the function to see whether the problem is fixed.
